\thesistitle

### 2019-07-22 sections/experimentalsetup.tex
Refactorability stuff

>>>>

\section{Method extraction opportunities}\label{sec:refactorabilitysetup}
The most used technique to refactor clones is method extraction (creating a new method on basis of the contents of clones). However, method extraction cannot be applied in all cases. In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.

We measured the number of clones that can be refactored through method extraction (without additional transformations being required). We defined the following categories:
\begin{itemize}
    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table~\ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
\end{itemize}

### 2019-07-22 sections/results.tex
Refactorability stuff

\section{Merging duplicate code through refactoring} \label{sec:refactorability}
The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones). However, method extraction cannot be applied in all cases. Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned). Merging the clones can be harder in such instances. Also, the cloned code can contain statements like \texttt{return}, \texttt{break}, \texttt{continue}. In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.

We measured the amount of clones that can be refactored through method extraction (without additional transformations being required). Our results are displayed in Table \ref{table:refactorability}. In this table we use the following categories:
\begin{itemize}
    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method. Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
\end{itemize}

@@

>>>>

\section{Merging duplicate code through refactoring} \label{sec:refactorability}
In section \ref{sec:refactorabilitysetup} we define catagories regarding the extent to which clones can be refactored through method extraction. Our results are displayed in Table \ref{table:refactorability}.

@@

\section{Refactoring clones}
\todo{TODO}
